\section{Business plan}
	\subsection{introduction}
	We take a responsible approach to finding sponsors. And also try to spend money effectively advance thinking through the details and equipment, finding ways to get them maximum benefit. Some sets we received as prizes in competitions.
	
	\subsection{Our sponsors and their support}
		\subsubsection{PTC and Irisoft}
		PTC and Irisoft representative in Russia is the one company that has helped us to begin to engage FTC providing the first set of Tetrx within the program's Score Thehnic which involved our Lyceum. They provide us with a different command symbols plus small gifts for other teams. They help us with the delivery of america. We use them programa Creo for creating 3D models. We also take part in events organized by them.
		\subsubsection{Robofinist}	
		Robofinist Charitable Foundation organized Temur Amindzhanovym and by Starline. They offered us its assistance as an organization in our city with outstanding achievements. They help to financially each month to give us 2000 Dolars, parts and equipment.
		\subsubsection{Robofinist}
		Volnoe Delo is one of the largest charitable foundations in Russia. It was established by Oleg Deripaska. We are participants in the program ROBOTOTEHNIKA.As support sent us free games field.They also engaged in training teachers and judges, including our own.Engaged in the organization of competitions FTC in Russia, is sponsoring a trip this year's winners have fully paying for a trip to St. Louis.	
		\subsubsection{Physics-Mathematics Lyceum №30}
		Physics-Mathematics Lyceum №30 a school in which my organization, it provides us with a comfortable space and material assistance, as well as leaders.
		
	\subsection{Purchase of materials.}
		\subsubsection{Our method}
		When we started robotics we had not a lot of money and we start from the fact that we have. Now the code we found sponsors, we first plan the details and equipment Ktorov we need to buy and then buy.Such an approach where we seek the materials on the basis of the decision proved to be a more than nahozhenie effectiveness solutions based on materials.
		\subsubsection{Our materials}
		As the center, we have 6 primary kits and 3 resource kits.We buy individual parts we need.At this point was made 2 large purchases for 1600 Dolar in November and March.
\newpage	