\subsubsection{04.04.15}
\begin{enumerate}
	
	\item The time of beginning and ending of the meeting: 16:00 - 22:00.
	
	\item Purposes of the meeting: 
	\begin{enumerate}
		
		\item To install blocks on the lift.
		
		\item To make a system with simultaneous lifting of the slats.
		
        \item To install Andy mark motors on the MEL.
		
	\end{enumerate}

	\item Work that has been done:
	\begin{enumerate}
		
		\item Blocks were installed with help of threads. Lift was tested. Result is positive. The force that we need for lifting much reduced. Also we compared сonstruction with the belt and construction with blocks with help of steelyard. Blocks give us the gain in force by a factor of 3-4.   
		
		\item It was decided to make MEL with 2 motors and transmission with gear ratio 2:1 and system with simultaneous lifting. It will give us the gain in speed by a factor of 1.5.
		
		\item MEL with gear ratio and Andy mark motors 2:1 was made.
		
        \item It was found that if we want to make a system with simultaneous lifting we need to make an individual mounts for rope that connect slats with each other. But it is too complicatedly and we haven't enough time for it. So it was decided to make MEL with 2 motors and gear ratio 1:2 without simultaneous lifting. It is less complicadly and give gain in speed by a factor 2. 

	\end{enumerate}
	
	\item Results:
	\begin{enumerate}
		
		\item Andy mark motors were installed on the MEL.
		
		\item Blocks were installed and tested.
		
		\item We found that blocks give gain in force by a factor 3-4.
		
		\item New construction of the lift and MEL was prokected.
		
	\end{enumerate}
	
	\item Tasks for the next meetings:
	\begin{enumerate}
		
		\item To make MEL with gear ratio 1:2.
		
		\item To install 2 additional motors for moving.
		
        \item To install transmission with gear ratio 1:2 on the motors that rotates wheels for more fast moving.
			
	\end{enumerate}
\end{enumerate}
\fillpage
