\subsubsection{01.04.15}
\begin{enumerate}
	
	\item The time of beginning and ending of the meeting: 19:00 - 21:30.
	
	\item Purposes of the meeting: 
	\begin{enumerate}
		
		\item Make a plan of tasks for the next 2,5 weeks before the championship in St. Louis.
		
	\end{enumerate}

	\item Work that has been done:
	\begin{enumerate}
		
		\item Today we discussed what changes and improvements with robot we'll do and in what order. Here is the final list of tasks:
		\begin{enumerate}
			\item 1-st priority:
			\begin{enumerate}
				
				\item Remove the majority of friction between slats from the lift to make it move easier.
				
				\item Install AndyMark motors instead of all DC motors.
				
				\item Use 6 motors for motion and make robot faster.
				
				\item Fix the wheels more reliably.
				
				\item Change the MEL for using 2 motors.
				
				\item Remove slopes for centering goals from the mechanism for capturing rolling goals.
				
				\item Buy new strong servos and fix them on MOB (2 servos) and on the capture for goals (1 servo).
				
				\item Replace the self-made wire on the lift with a standard one.
				
			\end{enumerate}
			
			\item 2-nd priority:
			\begin{enumerate}
				
				\item To make turning in autonomous period by giro.
				
				\item Automise working of the lift (4 positions: 0, 60, 90, 120 cm) and the gripper for balls.
				
				\item To make the video for nomination "Compass Award".
				
				\item Install the flexiglass protection to the front and back.
				
				\item Think about design of the pit at the competition and souvenirs for other teams.
				
			\end{enumerate}
			
			\item Low priority:
			\begin{enumerate}
				
				\item To make the mechanism that rise the rolling goal.
				
				\item Create a mechanism for pulling down the stick in autonomus period.
				
				\item Make autonomus program with IR for taking balls into the central goal.
				
			\end{enumerate}
		\end{enumerate}
		
	\end{enumerate}
	
	\item Results:
	\begin{enumerate}
		
		\item We made a detailed plan of tasks for the time before the competition in St. Louis.
		
	\end{enumerate}
	
	\item Tasks for the next meetings:
	\begin{enumerate}
		
		\item Follow the plan we made today.
			
	\end{enumerate}
\end{enumerate}
\fillpage
